### 2021-09-04 manuscript/methodology.tex
until "Detailed structure of matrices Axx, Ayy and Azz"

Now we can define the structure of $\mathbf{A}$ in terms of its components 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
let us consider that the observed total-field anomaly is located on an $N_{x} \times N_{y}$ 
regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
consequently, matrices $\mathbf{A}$ and $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ become 
square ($N \times N$). 
Besides, the horizontal coordinates $x_{i}$ and $y_{i}$ of the observation points 
can be defined by
\begin{equation}
x_{i} = x_{1} + \left[ k(i) - 1 \right] \, \Delta_{x}
\label{eq:xi}
\end{equation}
and
\begin{equation}
y_{i} = y_{1} + \left[ l(i) - 1 \right] \, \Delta_{y} \: ,
\label{eq:yi}
\end{equation}
where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
of the data grid (For details, please refer to \citet{takahashi2020convolutional}). 
For $x$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x}
\label{eq:k-x-oriented}
\end{equation}
and
\begin{equation}
l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil \: .
\label{eq:l-x-oriented}
\end{equation}
For $y$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: .
\label{eq:l-y-oriented}
\end{equation}
In equations \ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}, $\lceil \cdot \rceil$ denotes the ceiling 
function \citep[e.g.,][ p. 67-68]{graham-etal1994}.
Equations \ref{eq:xi}--\ref{eq:l-y-oriented} can also be used to define the coordinates 
$x_{j}$ and $y_{j}$ of the equivalent sources, but with index $j$ instead of $i$.

@@

%==================================================================================
\subsection{Matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in terms of block indices $q$ and $p$}
%==================================================================================

@@

In order to describe matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation
\ref{eq:A_expand}) in terms of block indices, we have to verify that:
(i) each pair of indices $i$ and $j$ produce a pair of block indices $q$ and $p$;
(ii) each element $a^{\alpha\beta}_{ij}$, defined by indices $i$ and $j$, can be 
represented by the alternative notation $a^{\alpha\beta}_{qp}$, defined in terms of
the associated block indices $q$ and $p$;
(iii) different combinations of indices $i$ and $j$ result in the same block indices $q$ and $p$; 
(iv) elements $a^{\alpha\beta}_{ij}$ having the same associated block indices $q$ and $p$
also have the same numerical value;
(v) matrix $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is formed by a grid of $Q \times Q$ blocks
$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, where each block has $P \times P$ elements
$a^{\alpha\beta}_{qp}$ with the same block index $q$;
(vi) blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ disposed along the same block diagonal 
of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ have the same block index $q$ and are equal to each other;
(vii) in each block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, the elements $a^{\alpha\beta}_{qp}$
having the same block index $p$ are arranged along the same diagonal and are equal to each other.

Item (i) is a direct consequence of evaluating equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}
for a given pair of indices $i$ and $j$. Item (ii) can be verified by substituting
the block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) 
into the second derivatives $h^{\alpha\beta}_{ij}$ 
(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) and then use them to
define the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}). The result
will be the elements $a^{\alpha\beta}_{qp}$. Item (iii) can be shown by first verifying that
different combinations of indices $i$ and $j$ result in the same integer functions
$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
Then, by using equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we conclude that
different combinations of $i$ and $j$ result in the same indices $q$ and $p$.
Item (iv) can be shown by noting that, according to equations 
\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, elements $a^{\alpha\beta}_{ij}$ having the same 
associated block indices $q$ and $p$ also have the same associated integer functions 
$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
As a consequence, the associated second derivatives $h^{\alpha\beta}_{ij}$ 
(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) have the same numerical values
and elements $a^{\alpha\beta}_{ij}$ as well. Items (v)-(vii) can be shown by computing the 
block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) for a small 
data grid formed by, say, $N_{x} = 3$, $N_{y} = 2$, and generalizing the result for larger grids.

From equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we can show that
the block index $q$ assume integer values varying from $-Q+1$ to $Q-1$, while 
$p$ varies from $-P+1$ to $P-1$. Positive (negative) indices $q$ are associated with blocks
$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ located below (above) the main block diagonal 
of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
Similarly, positive (negative) indices $p$ are associated with elements $a^{\alpha\beta}_{qp}$ 
located below (above) the main diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$.
According to this notation, $q$ defines the block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$
and $p$ the diagonal where the element $a^{\alpha\beta}_{qp}$ is located within this block, so that
matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
can be written, in a general form, as a grid of $Q \times Q$ blocks
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}   & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}   & \ddots          & \ddots          & \vdots           \\ 
\vdots           & \ddots          & \ddots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1}   \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{Q-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}  & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}
\end{bmatrix}_{N \times N} \: ,
\label{eq:BTTB_A_alpha_beta}
\end{equation}
with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ given by
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
a^{\alpha\beta}_{q0}   & a^{\alpha\beta}_{q(-1)} & \cdots  & a^{\alpha\beta}_{q(-P+1)} \\
a^{\alpha\beta}_{q1}   & \ddots     & \ddots  & \vdots       \\ 
\vdots      & \ddots     & \ddots  & a^{\alpha\beta}_{q(-1)}   \\
a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
\end{bmatrix}_{P \times P} \: .
\label{eq:Aq_block}
\end{equation}
This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
assumed by matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
(equation \ref{eq:A_expand}) is called Block-Toeplitz Toeplitz-Block (BTTB) 
\citep[e.g., ][ p. 67]{chan-jin2007}.

@@

%==================================================================================
\subsection{Structure of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%==================================================================================

Equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block} define the general BTTB
structure of all matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$, but 
there are some differences between them.
The integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and
\ref{eq:Delta_lij}) play a crucial role in defining the individual structures of matrix components 
$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).
These integer functions may assume positive and negative values depending on the relative
position of the observation point $(x_{i}, y_{i}, z_{0})$ and the equivalent source 
$(x_{j}, y_{j}, z_{c})$. 
%It is important noting that the structure of a given matrix component 
%$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is controlled by the numerator of the second derivatives
%$h^{\alpha\beta}_{ij}$ (equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}),
%$\alpha, \beta = x, y, z$, which are defined by the integer functions $\Delta k_{ij}$ and 
%$\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).

Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
$h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
\ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and $\mathbf{A}_{\boldsymbol{xx}}$ is symmetric.
Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
For $x$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-x-oriented} and 
\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be written as follows:
\begin{equation}
a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
\left( F_{x} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
\frac{1}{r_{qp}^{3}} \: ,
\label{eq:aqp_xx_x_oriented}
\end{equation}
where
\begin{equation}
\frac{1}{r_{qp}} = 
\frac{1}{\sqrt{\left( p \, \Delta_{x} \right)^{2} + \left( q \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
\label{eq:1_rqp_x_oriented}
\end{equation}
For $y$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-y-oriented} and 
\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be written as follows:
\begin{equation}
a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
\left( F_{x} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
\frac{1}{r_{qp}^{3}} \: ,
\label{eq:aqp_xx_y_oriented}
\end{equation}
where
\begin{equation}
\frac{1}{r_{qp}} = 
\frac{1}{\sqrt{\left( q \, \Delta_{x} \right)^{2} + \left( p \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
\label{eq:1_rqp_y_oriented}
\end{equation}
From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ for any grid orientation.
It means that the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$
and that they are symmetric. From this results we conclude the matrix component 
$\mathbf{A}_{\boldsymbol{xx}}$ is symmetric-Block-Toeplitz symmetric-Toeplitz-Block for any 
grid orientation.
The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
$\mathbf{A}_{\boldsymbol{zz}}$ also have this structure.

@@

% <========== in review

>>>>

Now we can define the structure of $\mathbf{A}$ in terms of its components 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
we consider the particular case in which the observed total-field anomaly is located 
on an $N_{x} \times N_{y}$ 
regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
consequently, matrices $\mathbf{A}$ and $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ become 
square ($N \times N$). 
Besides, the horizontal coordinates $x_{i}$ and $y_{i}$ of the observation points 
can be defined by
\begin{equation}
x_{i} = x_{1} + \left[ k(i) - 1 \right] \, \Delta_{x}
\label{eq:xi}
\end{equation}
and
\begin{equation}
y_{i} = y_{1} + \left[ l(i) - 1 \right] \, \Delta_{y} \: ,
\label{eq:yi}
\end{equation}
where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
of the data grid (Figure \ref{fig:regular-grids}). 
For $x$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x}
\label{eq:k-x-oriented}
\end{equation}
and
\begin{equation}
l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil \: .
\label{eq:l-x-oriented}
\end{equation}
For $y$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: .
\label{eq:l-y-oriented}
\end{equation}
In equations \ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}, $\lceil \cdot \rceil$ denotes the ceiling 
function \citep[e.g.,][ p. 67-68]{graham-etal1994}.
Equations \ref{eq:xi}--\ref{eq:l-y-oriented} can also be used to define the coordinates 
$x_{j}$ and $y_{j}$ of the equivalent sources, but with index $j$ instead of $i$.

@@

%=================================================================================
\subsection{General structure of matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%=================================================================================

@@

@@

Let us consider the small regular grid of $N_{x} = 3$ and $N_{y} = 2$ points shown by
Figure \ref{fig:regular-grids}. This grid may represent observation points 
$(x_{i}, y_{i}, z_{0})$ with constant vertical coordinate $z_{0}$ or equivalent sources
$(x_{j}, y_{j}, z_{c})$ with constant vertical coordinate $z_{c} > z_{0}$. In both cases,
the horizontal coordinates are defined by equations \ref{eq:xi} and \ref{eq:yi}.
Given an index $i$, associated with an observation point, and an index $j$, associated with
an equivalent source, we can compute $\Delta k_{ij}$ (equation \ref{eq:Delta_kij}), 
$\Delta l_{ij}$ (equation \ref{eq:Delta_lij}) and $\tfrac{1}{r_{ij}}$ 
(equation \ref{eq:1_rij_regular}). The matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ 
having elements $ij$ 
defined by $\Delta k_{ij}$ and $\Delta l_{ij}$, respectively, assume different forms, depending on
the grid orientation. For $x$-oriented grids, they are given by:
\begin{equation}
\Delta\mathbf{K} = \begin{bmatrix}
0 &  -1 &  -2 &   0 &  -1 &  -2 \\
1 &   0 &  -1 &   1 &   0 &  -1 \\
2 &   1 &   0 &   2 &   1 &   0 \\
0 &  -1 &  -2 &   0 &  -1 &  -2 \\
1 &   0 &  -1 &   1 &   0 &  -1 \\
2 &   1 &   0 &   2 &   1 &   0 \\
\end{bmatrix}
\label{eq:DK-matrix-x-oriented}
\end{equation}
and
\begin{equation}
\Delta\mathbf{L} = \begin{bmatrix}
0 &   0 &   0 &  -1 &  -1 &  -1 \\
0 &   0 &   0 &  -1 &  -1 &  -1 \\
0 &   0 &   0 &  -1 &  -1 &  -1 \\
1 &   1 &   1 &   0 &   0 &   0 \\
1 &   1 &   1 &   0 &   0 &   0 \\
1 &   1 &   1 &   0 &   0 &   0 \\
\end{bmatrix} \: .
\label{eq:DL-matrix-x-oriented}
\end{equation}
For $y$-oriented grids, they are given by:
\begin{equation}
\Delta\mathbf{K} = \begin{bmatrix}
0 &   0 &  -1 &  -1 &  -2 &  -2 \\
0 &   0 &  -1 &  -1 &  -2 &  -2 \\
1 &   1 &   0 &   0 &  -1 &  -1 \\
1 &   1 &   0 &   0 &  -1 &  -1 \\
2 &   2 &   1 &   1 &   0 &   0 \\
2 &   2 &   1 &   1 &   0 &   0 \\
\end{bmatrix}
\label{eq:DK-matrix-y-oriented}
\end{equation}
and
\begin{equation}
\Delta\mathbf{L} = \begin{bmatrix}
0 &  -1 &   0 &  -1 &   0 &  -1 \\
1 &   0 &   1 &   0 &   1 &   0 \\
0 &  -1 &   0 &  -1 &   0 &  -1 \\
1 &   0 &   1 &   0 &   1 &   0 \\
0 &  -1 &   0 &  -1 &   0 &  -1 \\
1 &   0 &   1 &   0 &   1 &   0 \\
\end{bmatrix} \: .
\label{eq:DL-matrix-y-oriented}
\end{equation}

These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
show that different combinations of indices $i$ and $j$ result in integer functions 
$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
having the same numerical value. In these cases, not only the numerical values of
the corresponding elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}),
but also their associated block indices $q$ and $p$ (equations 
\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) are the same. 
The contrary is also true: elements $a^{\alpha\beta}_{ij}$ having different 
associated block indices $q$ and $p$ also have different numerical values.
Because of that, using the alternative notation $a^{\alpha\beta}_{qp}$ to define the elements 
$a^{\alpha\beta}_{ij}$ in terms of its associated block indices $q$ and $p$ is a good
approach to investigate the structure of a given matrix component 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
This approach allows identifying elements $a^{\alpha\beta}_{ij}$ having the same numerical
value only by inspecting their associated block indices.

Note that, for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-x-oriented}) define the block indices
$p$ (equation \ref{eq:p-x-oriented}) and $q$ (equation \ref{eq:q-x-oriented}), respectively.
In this case, they are composed of $Q \times Q$ blocks with $P \times P$ elements each, where 
$Q = N_{y}$ and $P = N_{x}$. 
For $y$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-y-oriented})
and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-y-oriented}) define the block indices
$q$ (equation \ref{eq:q-y-oriented}) and $p$ (equation \ref{eq:p-y-oriented}), respectively.
In this case, they are also composed of $Q \times Q$ blocks with $P \times P$ elements each, 
but now $Q = N_{x}$ and $P = N_{y}$.
The examples shown by equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented}
also illustrate that, regardless of grid orientation, (i) the block index $q$ is constant 
inside each block; (ii) blocks disposed along the same block diagonal are equal to each other; 
(iii) the block index $p$ is constant on each diagonal of a given block; 
(iv) elements of a given block located on the same diagonal are also equal do each other.
Based on this well-defined structure of block indices, we can define 
matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in a general form
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}   & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}   & \ddots          & \ddots          & \vdots           \\ 
\vdots           & \ddots          & \ddots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1}   \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{Q-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}  & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}
\end{bmatrix}_{N \times N} \: ,
\label{eq:BTTB_A_alpha_beta}
\end{equation}
with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ given by
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
a^{\alpha\beta}_{q0}   & a^{\alpha\beta}_{q(-1)} & \cdots  & a^{\alpha\beta}_{q(-P+1)} \\
a^{\alpha\beta}_{q1}   & \ddots     & \ddots  & \vdots       \\ 
\vdots      & \ddots     & \ddots  & a^{\alpha\beta}_{q(-1)}   \\
a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
\end{bmatrix}_{P \times P} \: .
\label{eq:Aq_block}
\end{equation}
This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
(equation \ref{eq:A_expand}) is called Block-Toeplitz Toeplitz-Block (BTTB) 
\citep[e.g., ][ p. 67]{chan-jin2007}.

%=====================================================================================================
\subsection{Detailed structure of matrices $\mathbf{A_{xx}}$, $\mathbf{A_{yy}}$ and $\mathbf{A_{zz}}$}
%=====================================================================================================

Equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block} define the general BTTB
structure of all matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$, but 
there are some differences between them.
Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
$h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
\ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and we conclude that $\mathbf{A}_{\boldsymbol{xx}}$ 
is symmetric.
Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
For $x$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-x-oriented} and 
\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
\begin{equation}
a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
\left( F_{x} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
\frac{1}{r_{qp}^{3}} \: ,
\label{eq:aqp_xx_x_oriented}
\end{equation}
where
\begin{equation}
\frac{1}{r_{qp}} = 
\frac{1}{\sqrt{\left( p \, \Delta_{x} \right)^{2} + \left( q \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
\label{eq:1_rqp_x_oriented}
\end{equation}
For $y$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-y-oriented} and 
\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
\begin{equation}
a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
\left( F_{x} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
\frac{1}{r_{qp}^{3}} \: ,
\label{eq:aqp_xx_y_oriented}
\end{equation}
where
\begin{equation}
\frac{1}{r_{qp}} = 
\frac{1}{\sqrt{\left( q \, \Delta_{x} \right)^{2} + \left( p \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
\label{eq:1_rqp_y_oriented}
\end{equation}
From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and, consequently, that 
$\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$. We can also verify 
that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ and, consequently, that the blocks 
$\mathbf{A}_{\boldsymbol{xx}}^{q}$ are symmetric. Note that these symmetries are valid for 
any grid orientation.
From this results we conclude the matrix component 
$\mathbf{A}_{\boldsymbol{xx}}$ is symmetric-Block-Toeplitz symmetric-Toeplitz-Block for any 
grid orientation.
The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
$\mathbf{A}_{\boldsymbol{zz}}$ also have this symmetric structure.

@@
